%*******************************************************
% Acknowledgments
%*******************************************************
\pdfbookmark[1]{Acknowledgments}{acknowledgments}

\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgments}
During the time working on this dissertation, I had the pleasure to meet, work, and getting to know a large number of awesome people.

I would like to thank my supervisor Prof.~Dr\=/Ing.~Sebastian Möller for providing me the opportunity to pursue my doctoral degree.
Also, I would like to thank Prof.~Dr.~Judith Redi and Prof.~Dr.\=/Ing.~Ulrich Reiter for serving on my doctoral committee.

Also, I am grateful that I had the opportunity to work closely with Dr.~Benjamin Weiss, who provided important feedback, near-endless discussions, and his steady support.
The same holds for Prof.~Dr\=/Ing. Alexander Raake.

My deepest thanks goes to my colleagues and friends Anna Wunderlich and Frank Haase.
Without their impressive work, their clever ideas, and their precise preparation, the conducted experiments and thus this dissertation would have been impossible.
It felt like pure luxury working with them.
Thanks also to Henrique~Orefice for the opportunity to build an awesome software project.

I would also like to thank my colleagues and friends Friedemann Köster, Falk Schiffner, Steffen Zander, Janto Skowronek, Dr.~Hagen Wierstorf, Dr.\=/Ing.~Sebastian Arndt, Johannes Rummel, Prof.~Dr.\=/Ing. Jens Ahrens, and Dr.~Oliver Hohlfeld for introducing me to interesting topics, starting fancy research projects, and, most important, cheering me up.
Especially, the near-infinite number of table soccer games and the impressive niveau have been very important to me.

Last but not least, I am grateful to my girlfriend Regine Hähnel.
Without her energetic, continuous support, I would not have been able to finish this dissertation.
I am so glad, she endured all the stressful times and helped enthusiastically.

\bigskip
It was pleasure meeting you all and becoming part of my life.

\bigskip
Thanks.

\endgroup
